The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Finally, we display the morphology of the \textit{Fermi} bubbles\
 that emit gamma-rays from the inverse Compton scattering of ISRF by CRe\
 with the best-fit CRe sptral index 2.4

 We close on a speculative note that predicts an existence of a third bubbles for
 future observations.

@@

%  Having successfully reproduced the morphology\
%  and spectrum of the \textit{Fermi} bubbles,\
%  we now ask whether CRe could also explain\
%  the Galactic microwave haze.

@@

\Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
can also be realized by oblique jets as the eROSITA bubbles.\

>>>>

 Finally, \Cref{fig__gammaRay-map} shows the simulated gamma-ray photon flux compared with the observed one\
 in the energy bin $76.8-153.6$ GeV. One can see that the symmetric of the \textit{Fermi} bubbles\
 can also be realized by oblique jets as the eROSITA bubbles.\

 %We close on a speculative note that predicts an existence of a third bubbles for
 %future observations.

@@

@@
